Expected Dependency Pair Match:\\ Predicting improvements to {HTER} with expected syntactic structure

### 2009-05-08 mtjournal.tex
included correlations section from outline

>>>>

\section{Correlation with human judgments of fluency \& adequacy}

Corpus: LDC Multiple Translation Chinese corpus 3\&4 treat each
segment and each judgment as independent data point

\begin{itemize}
\item EXPT

  using n=1 parse for DPM variants

\begin{verbatim}
   metric      r
  --------   -----
  F[dl;lh]   0.226
  BLEU4      0.218  # +1 smoothing
  F[dlh]     0.185
  TER       -0.173
\end{verbatim}

  point: using partial-labeling (dl,lh) much better than full
  link. Also, using Charniak parser as labeler seems to work, LFG not
  necessary

\item EXPT

  combining precision, recall naively vs. combining items

\begin{verbatim}
  F(1g,2g,dl,lh)        0.237
  prmeans(1g,2g,dl,lh)  0.217

  F(dl,lh)              0.226
  prmeans(dl,lh)        0.208
\end{verbatim}

  point: combining individual items naively (before computing
  precision and recall) seems better than naively combining precisions
  and recalls (too many chances for zeroes?)

\item EXPT
  expanding n, gamma=0

\begin{verbatim}
  F[1g,2g,dl,lh],n=50   0.239
    ...          n=1    0.237
  F[dl,lh],n=50         0.234
    ...    n=1          0.226
\end{verbatim}
  point: larger n $\to$ better r
  (holds for other comparisons too, but these are good examples)

\item  EXPT

  setting gamma

  Tuning experiments finds that gamma of 0.25 is slightly better
  (especially when using F[dl,lh]) than gammas of other values in
  range 0-1 (these values probably not significant)

\end{itemize}
